\documentclass[11pt]{letter}
\usepackage[margin=25mm]{geometry}
\usepackage{hyperref}

\signature{Tobias Canavesi\\Independent Researcher\\\texttt{tobias.canavesi@crosschq.com}}
\address{Tobias Canavesi\\Independent Researcher}
\date{\today}

\begin{document}
\begin{letter}{Editorial Board\\Journal of Complex Networks\\Oxford University Press}

\opening{Dear Editors,}

I am writing to submit the manuscript entitled
\emph{``Semiprime Bottlenecks in Arithmetic Graphs: Betweenness Centrality from Prime Highways''}
for consideration in the Journal of Complex Networks.

The paper introduces a deterministic network family $G_N$ built on the integers
$\{1, \ldots, N\}$ with edges from sequential adjacency and prime-stride shortcuts.
The main result is a structural paradox: nodes with the highest degree (primorials)
are not the most central. Instead, betweenness centrality is dominated by semiprimes
$2p$ and $3p$, where $p$ is a large prime. We provide exact degree formulas,
a small-world diameter bound, a routing-theoretic explanation for the bottleneck
phenomenon, and computational verification up to $N = 10{,}000$.

The paper has not been submitted elsewhere and is not under consideration at any
other journal. There are no related preprints, dissertations, or previously published
papers containing similar content.

This is a single-author paper. I am an independent researcher and I have no
conflicts of interest to declare. No member of the Journal's editorial board
is an author of or contributor to this manuscript.

\medskip
\noindent\textbf{AI disclosure.}
The generative AI tool Claude Opus~4.6 (Anthropic, 2025) was used for assistance
with Python code development, figure generation, and \LaTeX{} formatting.
All mathematical content---including the graph definition, degree formula,
small-world bound, semiprime bottleneck theorem, and conjecture---is entirely
my original work. This use is disclosed in the Acknowledgements section of the
manuscript, as required by the Journal's AI policy.

\medskip
\noindent\textbf{Funding.}
This research received no specific grant from any funding agency.

\medskip
All code to reproduce the computations is publicly available at
\url{https://github.com/tobiascanavesi/arithmetic-graph-primes}.

Thank you for considering this submission.

\closing{Sincerely,}

\end{letter}
\end{document}
